\nextTopic{gd_01.latex} \chapter*{Preamble} One of the enchanting aspects of the natural sciences concerns the roles of {\em observation} and {\em generalization}. The subject matter of the  naturalsciences is often complex and, consequently, the source of endless fascination. However, this complexity, which requires documentationthrough careful observation and analysis,  may belie relatively simple   principles and symmetries (such as time invariance)   which govern thedynamics, and which can  only be understood by generalization and abstraction. \footnote{ In many ways these two different approaches  reflectthe differences between Aristotelian and Platonic world-views  as described  by Barrow  his excellent book {\em Pi in the sky} (Penguin, 1992) on theunreasonable effectiveness of mathematics  in the sciences.} In manyintriguing ways these two different approaches lead in opposing  directionsand  the    tension thus created   provides  the lifeblood of  our science.While the different approaches may require very different skills  andtemperaments, both are important to the development of our science, no one  more so than the other.  This course  fundamentally (andunashamedly) concerns the results and outcomes of  the process ofgeneralization (in which the Earth is necessarily considered   a very simplebeast responding to simple pleasures provided by the laws of nature). However,more than anythingelse, the questions addressed, and conclusions articulated, here represent thefruits of many hours spent observing at the outcrop scale where geology can appear very complex, indeed. While I believe  many benefits accrue from  the  world-view that results from the process of generalization, I begin with an important disclaimer:    careful observation and analysis will always be  remembered  and usedlong after once   fashionable interpretation has been ridiculed and disbanded.  After all,  the time-honored tradition of the sciences is that,like biological species,  theories   have a finite lifespan.\vspace{0.3in}\noindent Mike Sandiford, January 1994.  