---
title: "cv"
author: "Mike Sandiford"
date: "`r Sys.Date()`"
output:
  tufte::tufte_html: default
  tufte::tufte_handout: default
---
  
  
 
```{r setup, include=FALSE}
library(tufte)
knitr::opts_chunk$set(tidy = FALSE, cache.extra = packageVersion('tufte'))
options(htmltools.dir.version = FALSE)
library(stringr)
 library(scholar)
gs.id<-"qdYHZTgAAAAJ"
 my.cites=get_citation_history(gs.id)
 my.profile <- get_profile(gs.id)
 my.pubs1 <-get_publications(gs.id)
 
 gs <- function(title.str, pubs=my.pubs1, prefix= "citations "){
   sum.cites <- sum( pubs$cites[str_detect(str_to_lower(pubs$title), str_to_lower(title.str))])
   if (sum.cites > 0) paste(prefix,  sum.cites)
 } 
 
 
 tc.articles <- 53
 tc.readers <- 886000
# library(RSelenium)
# appURL <- "https://theconversation.com/profiles/mike-sandiford-228/dashboard"
# pJS <- phantom() # start phantomjs
# 
# remDr <- remoteDriver(browserName = "phantomjs")
# remDr$open()
# remDr$navigate(appURL)
# remDr$findElement("id", "user_email")$sendKeysToElement(list("mikes@unimelb.edu.au"))
# remDr$findElement("id", "user_password")$sendKeysToElement(list("1dMesH"))
# remDr$getCurrentUrl()
# 
# 
# webElem <-remDr$findElement(using = "class","primary")
# 
# webElem$sendKeysToElement(list("Enter", key = "enter"))
# 
# #remDr$screenshot(display = TRUE)
# 
# css.sel<-'//*[contains(concat( " ", @class, " " ), concat( " ", "readers", " " ))]//*[contains(concat( " ", @class, " " ), concat( " ", "league-gothic", " " ))]'
# my.readers <-remDr$findElement(using ='xpath', css.sel)
# tc.readers <-as.numeric(str_replace(my.readers$getElementText()[[1]], ",",""))
# 
# 
# css.sel<-'//*[contains(concat( " ", @class, " " ), concat( " ", "articles", " " ))]//*[contains(concat( " ", @class, " " ), concat( " ", "league-gothic", " " ))]'
# my.articles <-remDr$findElement(using ='xpath', css.sel)
# tc.articles <-as.numeric(str_replace(my.articles$getElementText()[[1]], ",",""))
# 
# pJS$stop()
# 
#  
```
***

 
#  1. Education and Employment History
## 1.1 Education
* PhD, `r margin_note("University of Melbourne")` 1985
* BSc(Hons), `r margin_note("University of Melbourne")` 1978

## 1.2 Current position

* Redmond Barry Distinguished Emeritus Professor, `r margin_note("University of Melbourne")` 2021

## 1.3 Previous Positions
* Redmond Barry Distinguished Professor, `r margin_note("University of Melbourne")` 2016-2021
* Chair of Geology, `r margin_note("University of Melbourne")` 2010-2021
* Director, Melbourne Energy Institute, `r margin_note("University of Melbourne")` 2009-2016
* ARC Professorial fellow, `r margin_note("University of Melbourne")` 2000-2009
* Lecturer/Senior Lecturer/Reader, `r margin_note("University of  Adelaide")` 1987-2000
* CSIRO postdoctoral fellow, `r margin_note("University of Cambridge")` 1986-1987

***
 
# 2. Recognition
## 2.1 Medals
* Carey Medal, 2014 `r margin_note("Geological Society of Australia")`  
* Hobbs Medal, 2012 `r margin_note("Geological Society of Australia")`  
* Mawson Medal, 2005  `r margin_note("Australian Academy of Sciences")` 
* Stillwell Medal(s), 2003, 2005 and 2009 `r margin_note("Geological Society of Australia")` 

## 2.2 Fellowships 
* Elected Fellow, Australian Academy of Sciences, 2013 `r margin_note("Australian Academy of Sciences")` 
* Elected Fellow, Geological Society of Australia, 2011 `r margin_note("Geological Society of Australia")`
* Distinguished Visiting Professor, Paris, France,  2008 `r margin_note("Ecole Normale Supérieure")` 
* ARC Professorial Fellow, 2005-2009 `r margin_note("Australian Research Council")`
* ARC Professorial Fellow, 2000-2004 `r margin_note("Australian Research Council")`
* CSIRO Postdoctoral Fellowship, Cambridge University, 1986-1987 `r margin_note("Cambridge University")`


 
***
# 3. Professional Service
## 3.1 Editorial  boards
* Tectonophysics, Co Editor-in-Chief, 2004-2009
* Geology, Editorial Board, 1999-2001 and  2009-2011
* Australian Journal of Earth Science, 2005-2008

## 3.2  Advisory boards, Review panels, Expert advisory roles
* Expert Advisor to the NSW Energy security taskforce, 2017 `r margin_note("NSW Office of Chief Scientist")`
* IMAGE project review, Iceland, 2017 `r margin_note("European Commission")`
* IMAGE project review, Italy, 2015 `r margin_note("European Commission")`
* Review of Geosciences Victoria University, NZ,  2015  `r margin_note("Victoria University, NZ")`
* Review of Kedarnath landslide disaster, India, May 2014. `r margin_note("Indian Department Science and Technology")`
* Strategic roadmap for Australian Research Infrastructure, 2011 `r margin_note("Department Industry, Australian Federal Government")`
* ARC College of Experts, 2009-2011 `r margin_note("Australian Research Council")`
* IPGT `r margin_note("International Partnership for Geothermal Technology")` Exploration technologies working group, 2010-2012 
* EON Research Centre, Science Advisory Board, 2011-2012  `r margin_note("RWTH Aachen Germany")`
* SUNConnect Advisory Board, 2011 `r margin_note("Melbourne, Australia")`
* AuScope-AGOS EIF Science Advisor, 2009-2013 `r margin_note("Melbourne, Australia")`
* AuScope Science Advisory Board (Chair), 2007-2012 `r margin_note("Melbourne, Australia")`
* PMD*CRC Science Advisory Board, 2000-2002 `r margin_note("Melbourne, Australia")`

***
 
# 4. Research programs and funding (since 2000)


 
## 4.1 Competitive Research Program Grants 
*   Causes of high geothermal gradient metamorphism at Mount Painter, CI Sandiford, ARC Discovery, 2000-2001 `r margin_note("\\$255,000 ")`
*    Heat production, tectonic feedback and the shaping of the Australian continent, CI Sandiford, ARC professorial Fellowship, 2000-2004 `r margin_note("\\$519,000")`
*   Tectonic feedback and the long-term evolution of the continents, CI Sandiford, 2002-2004 `r margin_note("\\$251,000")`
*   Neotectonics of the Indo-Australian plate, CI Sandiford, ARC Discovery and Professorial Fellowship, 2005-2009 `r margin_note("\\$1,051,000")` 
*   Murray Basin: A unique archive of late Neogene global change, - CI’s Wallace, Sandiford, Gallagher, ARC Discovery, 2005-2007 `r margin_note("\\$296,000")`
*   3D Computational models of geological basin and hinterland evolution incorporating lithospheric mantle and surface processes, CI’s Moresi, Sandiford, Powell, Karner, ARC Linkage, 2007-2010 `r margin_note("\\$265,000")`
*   Thermal structure and evolution of the Australian Continent, CI’s McLaren, Sandiford, ARC Discovery, 2009-2013 `r margin_note("\\$855,000")`
*   Active tectonics of East Timor: geomorphic responses to an evolving slab rupture, CI Sandiford, ARC Discovery, 2011-2013 `r margin_note("\\$300,000")`
*   Indo-Australian plate Active tectonics program, CI Sandiford,  ARC Discovery, 2014-2016 `r margin_note("\\$400,000")`
*   Earthquake hazard map for Victoria, CI’s  Rawling, Sandiford, NDRG, 2011-2013 `r margin_note("\\$150,000")`
*   Characterization of the seismic cycle in the central Himalayan seismic gap using precise U-Th dating of deformed speleothems,  CI’s Sandiford, Woodhead, AIRSRF, 2011-2012 `r margin_note("\\$225,000")`
*   Optimisation of Earthquake Monitoring for CCS Applications on Local and Microearthquake Scales,  CI Sandiford, ANLEC R\&D, 2017-2019 `r margin_note("\\$658,156")`

__Sub total__ `r margin_note("\\$5,474,156" )`

## 4.2 Infrastructure grants - University of Melbourne
*  Carbonnet - GIPnet seismic network, EIF Clean Energy,  2015-2018 `r margin_note("\\$ 1,250,000")`
*  AGOS Subsurface Observatory, EIF round 3, 2011-2014 `r margin_note("\\$ 6,700,000")` 

*  Surface Process Modelling	CI Sandiford, ACCESS MNRF, 2003-2007 `r margin_note("\\$ 393,000")`	

__Sub total__ `r margin_note("\\$8,343,000" )`

## 4.3 Infrastructure grants - other universities
*  Investigating the Structure and Evolution of the Continental Crust: A Virtual Facility for Thermochronology, Noble Gas Geochemistry and Geochronology,  CI’s Vasconcelas et al., ARC LIEF, 2008 `r margin_note("\\$ 650,000")` 
*   An advanced, macro-scale, hydro-thermo-mechanical testing chamber for sustainable deep geological applications, CI’s Ranjith et al., ARC LIEF, 2012 `r margin_note("\\$ 940,000")`
*   A new seismic facility for investigating tectonic collision zones, earthquake hazards and passive imaging techniques” CI’s Rawlinson et al., ARC LIEF, 2013 `r margin_note("\\$ 285,000")`

__Sub total__ `r margin_note("\\$1,875,000" )`

## 4.4 Other significant funding

*  Geodynamic groundwater, Geoscience Australia, 2014-2016  `r margin_note("\\$ 405,000")`
*  Zero Carbon Australia,   Graeme Wood Foundation, 2010-2012 `r margin_note("\\$ 350,000")`
*  Novel carbon capture, ANLECC, 2012 `r margin_note("\\$ 150,000")`
*  Centre for	Centre for geological carbon storage,   DPI 	`r margin_note("\\$ 750,000")` ,2011-2014
*  Director AGOS Infrastructure,	 AuScope, 2011-2016 `r margin_note("\\$ 697,000")`
*  Subsurface Observatory,	 AuScope, 2015-2018 `r margin_note("\\$ 550,000")`

__Sub total__ `r margin_note("\\$2,857,000" )`

__Total funding __ `r margin_note("\\$17,948,156" )`


# 5. Scholarly works 

## 5.1. Citation metrics 

Google Scholar

`r  
#library(scholar)
#gs.id<-"qdYHZTgAAAAJ"
#my.profile <- get_profile(gs.id)
 paste("Total citations - ", my.profile$total_cites, "\n\n ", "Hirsch-index - ", my.profile$h_index, "\n\n ","i10-index - ", my.profile$i10_index) 
`

```{r fig-margin1, fig.margin = TRUE,  echo=FALSE ,   fig.align="right"} 
#library(scholar)
library(ggplot2)
#gs.id<-"qdYHZTgAAAAJ"
 
#my.cites=get_citation_history(gs.id)
ggplot(my.cites, aes (year, cites))+geom_bar(stat="identity" ) +ylab("google scholar cites")
```
## 5.2 Peer-reviewed publications

1.  Rosenbaum, G.,  __Sandiford, M.__,  Caulfield, J.,  Garrison, J.M., in press,  A trapdoor mechanism for slab tearing and melt generation in the northern Andes, Geology,  doi:10.1130/G45429.1. 
`r margin_note( gs("A trapdoor mechanism for slab tearing"))`

1. Li, G.,  Kohn, B., __Sandiford, M.__, Ma, Z., Xu ,Z., 2018, Post-collisional exhumation of the Indus-Yarlung suture zone and Northern Tethyan Himalaya, SW Tibet, Gondwana Research 64, 1-10. doi:10.1016/j.gr.2018.06.006 
`r margin_note( gs("Post-collisional exhumation of the Indus-Yarlung suture zone"))`

1. Hoffman, N., Hardman-Mountford, N.,   Jenkins, C.,  Rayner,P.J.,  Gibson, G.,  __Sandiford, M.__, 2017, GipNet–Baseline Environmental Data Gathering and Measurement Technology Validation for Nearshore Marine Carbon Storage, Energy Procedia 114, 3729-3753. doi:10.1016/j.egypro.2017.03.1503. 
`r margin_note( gs("GipNet–Baseline Environmental Data Gathering"))`

1. Beardsmore, G., __Sandiford, M.__,  Gordon, K.,  McLean, M., Egan, S. McLaren, S., 2017, Heat flow and inferred ground surface temperature history at Tynong North, southeastern Australia,  Australian Journal of Earth Sciences, 64, 753-767, doi:10.1080/08120099.2017.1362663.
`r margin_note( gs("Heat flow and inferred ground surface temperature history at Tynong"))`

1.  Morell, K.D., __Sandiford, M.__,   Kohn, B.,  Codilean, A., Folup, R.,  Ahmad, T., 2017, Current strain accumulation in the hinterland of the northwest Himalaya, Tectonophysics,  721, 70-89, doi:10.1016/j.tecto.2017.09.007. 
`r margin_note( gs("strain accumulation in the hinterland of the northwest Himalaya"))`

1. Li, G.,  Kohn, B., __Sandiford, M.__, Xu ,Z., 2017, India-Asia convergence: Insights from burial and exhumation of the Xigaze forearc basin, south Tibet, Journal of Geophysical Research, 122, doi:10.1002/2017JB014080. `r margin_note( gs("India‐Asia convergence: Insights from burial"))`

1.	Boger, S.D.,  Spelbrink, L.G., Lee, R.I., __Sandiford, M.__, Maas, R., Woodhead, J.D., 2017, Isotopic (U-Pb, Nd) and geochemical constraints on the origins of the Aileu and Gondwana sequences of Timor,   Journal of Asian Earth Sciences, 134, 330-351, doi:10.1016/j.jseaes.2016.11.026. `r margin_note( gs("geochemical constraints on the origins of the Aileu and Gondwana sequences of Timor"))`
1.	Li, G.,  Kohn, B., __Sandiford, M.__, Xu ,Z., Seiler, C., Tian, Y., 2016, Synorogenic morphotectonic evolution of the Gangdese batholith, South Tibet: Insights from low-temperature Thermochronology,  Geochemistry, Geophysics, Geosystems 17, 101-112. doi:10.1002/2015GC006047. `r margin_note( gs("Synorogenic morphotectonic evolution"))`
1. Lawrie, K., Brodie,  R.S. Christensen, N.,   Gibson, D.,  Halas, L., Symington, N., Tan,K.,   __Sandiford, M.__,   Ziramov, S.,  Urosevic, M., Grunewald, E.,   Hayes,P. 2016, Neotectonic Intra-Plate Fault Zone Mapping and Hydrogeology in Floodplain Sediments: An Inter-Disciplinary Approach, ASEG Extended Abstracts 2016, 1-9, doi:10.1071/ASEG2016ab400. `r margin_note( gs("fault zone mapping and hydrogeology"))`
2.	Rajendran. C.P., Sanwal, J., Morell, K.D., __Sandiford, M.__, Kotlia, B.S., Hellstrom, J., Rajendran, K., 2016, Stalagmite growth perturbations from the Kumaun Himalaya as potential earthquake recorders, Journal of Seismology, 20, 579-594. `r margin_note( gs("Stalagmite growth"))`
3.	McConnell, D., Forcey, T., __Sandiford, M.__, 2015, Estimating the value of electricity storage in an energy-only wholesale market, Applied Energy, 159, 422-432  doi:10.1016/j.apenergy.2015.09.006.  `r margin_note(  gs("value of electricity storage"))`
1.	Coblentz, D., van Wijk, J., Richardson, R.M., __Sandiford, M.__, 2015, The Upper Mantle Geoid: Implications for Continental Structure and the Intraplate Stress Field. The Interdisciplinary Earth: A volume in honor of Don L. Anderson, Geological Society of America Special Paper 514,  197-214, ed. G.R. Foulger, M. Lustrino and S. King.  doi:10.1130/2015.2514(13)   `r margin_note( gs("Upper Mantle Geoid"))`
1.	__Sandiford, M.__, Forcey, T., Pears, A., McConnell, D., 2015, Five years of declining annual consumption of grid-supplied electricity in eastern Australia: causes and consequences, The Electricity Journal, 28, 96-117, doi:10.1016/j.tej.2015.07.007  `r margin_note( gs("Five years"))`
1.	Li, G., Kohn, B., __Sandiford, M.__, Xu, Z., We, L., 2015, Constraining the age of Liuqu Conglomerate, southern Tibet: Implications for evolution of the India-Asia collision zone. Earth and Planetary Science Letters, 426, 259-266, doi:10.1016/j.epsl.2015.06.010 `r margin_note( gs("Liuqu"))`
1.	Li, G., Tian, Y., Kohn, B.P., __Sandiford, M.__, Xu, Z.,Ca, Z., 2015, Cenozoic low temperature cooling history of the Northern Tethyan Himalaya in Zedang, SE Tibet and its implications, Tectonophysics, doi:10.1016/j.tecto.2014.12.014 `r margin_note( gs("Zedang"))` 
1.	Li., G., __Sandiford, M.__, Boger, S., Liu, X.., Wei, L., 2015, Provenance of the Upper-Cretaceous to Lower Tertiary sedimentary relicts in the Renbu mélange zone, within the Indus-Yarlung suture zone, Journal of Geology, 123, 39–54, doi:10.1086/680207  `r margin_note( gs("Renbu"))`
1.	Morell, K.D., __Sandiford, M.__, Rajendran, C.P., Rajendran, K., Fink, D., Alimanovic, A., Sanwal, J., 2015, Geomorphology reveals active decollement geometry in the central Himalayan seismic gap, Lithosphere, 7, 247-256, doi:10.1130/L407.1  `r margin_note( gs("geometry in the central"))`
1.	Ely, K.S., __Sandiford, M.__, Phillips, D., Boger, S.D., 2014, Detrital zircon U-Pb and 40Ar/39Ar hornblende ages from the Aileu Complex, Timor-Leste: provenance and metamorphic cooling history, Journal of the Geological Society of London, doi: 10.1144/jgs2012-065 `r margin_note( gs("Aileu Complex"))`
1.	Holford, S., Tuitt, A., Hillis, R., Green, P., Stoker, M., Duddy, I., __Sandiford, M.__, Tassone, D., 2014, Cenozoic deformation in the Otway Basin, southern Australian margin: implications for the origin and nature of post-breakup compression at rifted margins, Basin Research, 26, 10–37, doi: 10.1111/bre.12035  `r margin_note( gs("deformation in the Otway Basin"))`
1.	Li, G., __Sandiford, M.__, Liu, X., Xu, Z., We, L., Li. H., 2014, Provenance of the Late Triassic sediments in Central Lhasa terrane, Tibet, and its implication, Gondwana Research, doi:10.1016/j.gr.2013.06.019 
`r margin_note( gs("Central Lhasa terrane"))`
1.	Rawling, T.J., __Sandiford, M.__, Beardsmore, G.R., Quenette, S., Goyen, S.H., Harrison, B., 2014, Thermal insulation and geothermal targeting, with specific reference to coal-bearing basins, Australian Journal of Earth Sciences, 60, 817-830, doi:10.1080/08120099.2013.864999 `r margin_note( gs("Thermal insulation"))`
1.	Rajendran, C.P., Rajendran, K., Sanwal, J., __Sandiford, M.__, 2013, Archeological and historical database on the medieval earthquakes of the central Himalaya: Ambiguities and Inferences, Seismological Research Letters, 84, 1098-1108, doi: 10.1785/0220130077 `r margin_note( gs("Archeological and historical"))` 
1.	Egholm, D., Knusden, M.F., __Sandiford, M.__, 2013, Lifespan of mountain ranges scaled by feedbacks between landsliding and erosion by rivers, Nature, 498, 475–478, doi:10:1038/nature12218 
`r margin_note( gs("Lifespan of mountain ranges"))` 
1.	Sanwal, J., Kotlia, B.S., Rajendran, C.P., Ahmad, S., Rajendran, K., and __Sandiford, M.__, 2013, Climate variability in Central Indian Himalaya during the last ~1,800 years: Evidence from high resolution speleothem record, Quaternary International, 304, 183–192, doi:/10.1016/j.quaint.2013.03.029  `r margin_note( gs("Central Indian"))`
1.	McConnell, D., Hearps, P., Eales, D., __Sandiford, M.__, Dunn, R., Wright, M., Bateman, L., 2013, Retrospective modeling of the merit-order effect on wholesale electricity prices from distributed photovoltaic generation in the Australian National Electricity Market, Energy Policy, 58,17-27, doi:10.1016/j.enpol.2013.01.052 
`r margin_note(  gs("Retrospective modeling of the"))`
1.	Shin, J., __Sandiford, M.__, 2012, Neogene uplift in the Korean peninsula linked to small-scale mantle convection at sinking slab edge. Journal of Korean Geographical Society, 47(3), 328-346 
1.	Turner, S., Caulfield, J., Turner, M., van Keken, P., Maury, R., __Sandiford, M.__, Prouteau, G., 2012, Recent contribution of sediments and fluids to the mantle’s volatile budget, Nature geoscience, 5, 50-54, doi:10.1038/ngeo1325 `r margin_note( gs("Recent contribution of sediments"))`
20.	Long, A., Budd, A., Gurgenci,H., Hand,M., Huddlestone-Holmes, C., Leary ,P., Malin, P., Moghtaderi,B., Regenauer-Lieb,K., __Sandiford, M.__, Webster, R., 2011, Australian geothermal research 2011, Proceedings, Thirty-Sixth Workshop on Geothermal Reservoir Engineering, Stanford University, Stanford, California, January 31 - February 2, 2011, SGP-TR-191
1.	Clark, D., Cupper, M., __Sandiford, M.__, Kiernan, K., 2011, Style and timing of late Quaternary faulting on the lake Edgar Fault, southwest Tasmania, Australia: implications for hazard assessment in intracratonic areas, In: \\$emard, F., Michetti, A., Macalpin, J. (eds) Geological criteria for evaluating seismicity revisited: 40 years of paleoseismic investigations and the natural record of past earthquakes, Geological Society of AmericaSpecial Papers, 479, 109-131, doi:10.1130/2011.2479(05) 
`r margin_note(  gs("Edgar Fault"))`
1.	Ely, K.S., __Sandiford, M.__, Hawke, M.L., Phillips, D., Quigley, M., dos Reis, J.E., Evolution of Ataúro Island: temporal constraints on subduction processes beneath the Wetar Zone, Banda Arc , Journal of Asian Earth sciences, doi:10.1016/j.jseaes.2011.01.019 `r margin_note( gs("temporal constraints on subduction processes"))`
1.	Holford, S.P., Hillis, R.R., Hand, M. and __Sandiford, M.__, 2011, Thermal weakening localizes intraplate deformation along the southern Australian continental margin, Earth and Planetary Science Letters, 305, 217-214, doi:10.1016/j.epsl.2011.02.056 `r margin_note( gs("Thermal weakening localizes intraplate deformation along the southern"))`
1.	Fu,B., Walker, R., __Sandiford, M.__, 2011, The 2008 Wenchuan earthquake and active tectonics of Asia, Journal of Asian Earth Sciences, 40, 797-804 
`r margin_note(  gs("Wenchuan"))`
1.	Jakica, S, Quigley, M., __Sandiford, M.__, Clark, D., Fifield, L.K., Alimanovic, A., 2011, Geomorphic and cosmogenic nuclide constraints on escarpment evolution in an intraplate setting, Darling Escarpment, Western Australia,  Earth Surface Processes and Landforms, 36, 449-459, doi:10.1002/esp.2058 `r margin_note( gs("constraints on escarpment evolution"))`
1.	Turner, S., __Sandiford, M.__, Regan, M., Hawkesworth, C., Hildreth, W., 2010, The origins of large volume, compositionally-zoned volcanic eruptions - new constraints from U-series isotopes and numerical thermal modeling for the 1912 Katmai-Novarupta eruption, Journal of Geophysical Research, 115, B12201, doi:10.1029/2009JB007195 `r margin_note( gs("Katmai"))`
29.	Quigley, M.C., Clark, D., __Sandiford, M.__, 2010, Tectonic geomorphology of Australia, In: Bishop, P., Pillans, B. (eds) Australian Landscapes. Geological Society, London, Special Publications, 346, 243-265 
`r margin_note( gs("Tectonic geomorphology of Australia"))`
30.	Quigley, M., Horton, T., Hellstrom, J., Cupper, M., __Sandiford, M.__, 2010, Holocene precipitation variability in arid Australia from speleothem and alluvial records, The Holocene, doi:10.1177/0959683610369508
`r margin_note( gs("arid Australia"))`
31.	__Sandiford, M.__, 2010, Complex Subduction, Nature Geoscience, 3, 518-520, doi:10.1038/ngeo928
`r margin_note(  gs("Complex Subduction"))`
32.	Brown, M., White, R.W., __Sandiford, M.__, 2010, On the importance of minding one's Ps and Ts: Metamorphic processes and quantitative petrology, Journal of Metamorphic Geology, 28, 561–567, doi:10.1111/j.1525-1314.2010.00892.x  `r margin_note( gs("On the importance of minding"))`", 
33.	__Sandiford, M.__, 2010, Why are the continents just so ...?, Journal of Metamorphic Geology, 28, 569–577  doi:10.1111/j.1525-1314.2010.00888.x 
`r margin_note(  gs("Why are the continents just so"))`
34.	Farrington, R., Stegman, D., Moresi, L.N., __Sandiford, M.__, May, D., 2010, Interactions of 3D mantle flow and continental lithosphere near passive margins, Tectonophysics, 483, 20-28  doi:10.1016/j.tecto.2009.10.008
`r margin_note(  gs("Interactions of 3D mantle flow"))`
35.	Ely, K., __Sandiford, M.__, 2010, Seismic response to slab rupture and variation in lithospheric structure beneath the Savu Sea, Indonesia, Tectonophysics, 483, 112-124, doi:10.1016/j.tecto.2009.08.027
`r margin_note(  gs("Seismic response to slab rupture"))`
36.	Woodhead, J., Hergt, J., __Sandiford, M.__, Johnson, W., 2010, The big crunch: physical and chemical expressions of arc/continent collision in the western Bismarck arc, Journal of Volcanology and Geothermal Research, 190, 11-24  doi:10.1016/j.jvolgeores.2009.03.003 
`r margin_note(  gs("The big crunch"))`
37.	Quigley M. C., __Sandiford, M.__, Clark, D., 2009, Neotectonics and landscape evolution of southeastern Australia: establishing a geologic context for contemporary seismicity, In: Clark, D., (ed), Potential geologic sources of seismic hazard in the Sydney Basin. Geoscience Australia Record 2009/11, 1-6 
38.	__Sandiford, M.__, Quigley, M., de Broekert, P., Jakica, S., 2009, Tectonic framework for the Cenozoic cratonic basins of Australia, Australian Journal of Earth Sciences, 56, S5-S18, doi:10.1080/08120090902870764 
`r margin_note( gs("Tectonic framework for the Cenozoic cratonic basins of Australia"))`
39.	Turner,S., Haines, P., Foster, D, Powell R., __Sandiford, M.__, Offler, R.,2009, Did the Delamerian Orogeny start in the Neoproterozoic? Journal of Geology, 117, 575-583 
`r margin_note( gs("Did the Delamerian Orogeny start in the Neoproterozoic? Journal of Geology"))`
40.	Braun, J., Burbidge, D.R., Gesto, F.N., __Sandiford, M.__, Gleadow, A.J.W., Kohn, B.P., Cummins, P.R., 2009, Constraints on the current rate of deformation and surface uplift of the Australian continent from a new seismic database and low-T thermochronological data. Australian Journal of Earth Sciences, 56, 99-110  doi:10.1080/08120090802546977 
`r margin_note( gs("current rate of deformation and surface uplift"))`
41.	McLaren, S., __Sandiford, M.__, Dunlap, W.J., Scrimgeour, I., Close, D. and Edgoose, C., 2009, Distribution of Palaeozoic reworking in the Western Arunta province and northwestern Amadeus Basin from 40Ar/39Ar thermochronology: implications for the evolution of intracratonic basins, Basin Research, 21, 315-334  doi:10.1111/j.1365-2117.2008.00385.x 
`r margin_note(  gs("Western Arunta"))
` 
42.	__Sandiford, M.__, Quigley,M.C., 2009, TOPO-OZ: insights into the various modes of intraplate deformation in the Australian continent, Tectonophysics, 474, 405-416  doi:10.1016/j.tecto.2009.01.028 
`r margin_note(  gs( "TOPO-OZ"))`
43.	Somerville, P., Quijada, P., Hong Kie Thio, __Sandiford, M.__, Quigley, M., 2008, Contribution of identified active faults to near fault seismic hazard in the Flinders Ranges, Australian Earthquake Engineering Society Conference Proceedings, Paper 45, 1-9.
1.	Egholm, D.L., Clausen, O.R., __Sandiford, M.__, Kristensen, M.B., Korstgard, J.A., 2008, The mechanics of clay smearing along faults, Geology, 36, 787–790  doi:0.1130/G24975A.1
`r margin_note( gs("mechanics of clay smearing"))`
1.	Hillis, R.R., __Sandiford, M.__, Reynolds, S.D. and Quigley, M.C., 2008, Present-day stresses, seismicity and Neogene-to-Recent tectonics of Australia’s ‘passive’ margins: intraplate deformation controlled by plate boundary forces. In: Johnson, H., Dore, A. G., Gatliff, R. W., Holdsworth, R., Lundin, E. and Ritchie, J. D. (eds) The Nature and Origin of Compression in Passive Margins. Geological Society, London, Special Publications, 306, 71–89  doi:10.1144/SP306.3 
`r margin_note(  gs("intraplate deformation controlled by plate boundary forces"))`
1.	__Sandiford, M.__, Egholm, D.L., 2008, Enhanced intraplate seismicity along continental margins: some causes and consequences, Tectonophysics, 457, 197–208, doi:10.1016/j.tecto.2008.06.004 
`r margin_note(  gs("Enhanced intraplate seismicity along"))`
1.	Quigley, M.C., Yu Liangjun, Gregory, C., Corvino, A., __Sandiford, M.__, Wilson, C.J.L., Liu Xiaohan, 2008, U-Pb SHRIMP zircon geochronology and T-t-d history of the Kampa Dome, southern Tibet, Tectonophysics, 446, 97-113  doi:10.1016/j.tecto.2007.11.004 
`r margin_note(  gs("history of the Kampa Dome"))`
1.	Dosseto, A., Turner, S.P., __Sandiford, M.__, Davidson, J., 2008, Uranium-series isotope and thermal constraints on the rate and depth of silicic magma genesis, In: Dynamics of Crustal Magma Transfer, Storage and Differentiation, Annen C. and Zellmer, G.F. (eds). Geological Society of London Special Publication, 304, 169-181 
`r margin_note(  gs("depth of silicic magma genesis"))
` 
1.	Hou, B., Frakes, L.A., __Sandiford, M.__, Worrall, L., Keeling, J., Alley, N.F., 2008, Cenozoic Eucla Basin and associated palaeovalleys, southern Australia - climatic and tectonic influences on landscape evolution, sedimentation and heavy mineral accumulation, Sedimentary Geology, 203, 112-130  doi: 10.1016/j.sedgeo.2007.11.005 
`r margin_note(  gs("Cenozoic Eucla Basin"))`
1.	__Sandiford, M.__, 2008, Seismic moment release during slab rupture beneath the Banda Sea, Geophysical Journal International, 174, 659–671  doi: 10.1111/j.1365-246X.2008.03838.x 
`r margin_note(  gs("slab rupture beneath the Banda Sea"))`
1.	Bowler, J.M., __Sandiford, M.__, 2007, Dynamic Antarctic Ice: agent for Mid-Pleistocene Transition, PAGESnews, 15, 16-18
`r margin_note(  gs("Dynamic Antarctic"))
` 
1.	Quigley, M., __Sandiford, M.__, Cupper, M., 2007, Distinguishing tectonic from climatic controls on range-front sedimentation, Flinders Ranges, South Australia. Basin Research, 19, 491–505  doi: 10.1111/j.1365-2117.2007.00336.x 
`r margin_note(  gs("Distinguishing tectonic from climatic"))`
1.	Demidjuk, Z., Turner, S., __Sandiford, M.__, George, R., Foden, J., Etheridge, M., 2007, U-series isotope and geodynamic constraints on mantle melting processes beneath the Newer Volcanic Province in South Australia, Earth and Planetary Science Letters, 261, 517–533  doi: 10.1016/j.epsl.2007.07.006 
`r margin_note(  gs("isotope and geodynamic constraints on mantle melting processes beneath the Newer Volcanic Province in South Australia"))` 
1.	__Sandiford, M.__, 2007, The tilting continent: a new constraint on the dynamic topographic field from Australia, Earth and Planetary Science Letters, 261, 152-163  doi: 10.1016/j.epsl.2007.06.023 
`r margin_note(  gs("The tilting continent"))` 
1.	Quigley, M., __Sandiford, M.__, Alimanovic, A., Fifield, L.K., 2007, Landscape responses to intraplate tectonism in the Flinders Ranges, South Australia: quantitative constraints from 10Be abundances, Earth and Planetary Science Letters, 261,120-133  doi:10.1016/j.epsl.2007.06.020
`r margin_note(  gs( "Landscape responses to intraplate tectonism"))` 
1.	Egholm, D.L., __Sandiford, M.__, Clausen, O.L., Nielsen, S.B., 2007, A new strategy for discrete element numerical models Part II: Sandbox applications, Journal of Geophysical Research, 112, B05204  doi:10.1029/2006JB004558 `r margin_note(  gs( "A new strategy for discrete element"))` 
1.	Quigley, M., __Sandiford, M.__, Fifield, K., Alimanovic A., 2007, Bedrock erosion and relief production in the northern Flinders Ranges, Australia. Earth Surface Processes and Landforms, 32, 929-944  doi: 10.1002/esp.1459 
`r margin_note(  gs("Bedrock erosion and relief production"))` 
1.	McLaren, S., __Sandiford, M.__, Powell, R., Neumann, N., Woodhead, J., 2006, Palaeozoic intraplate crustal anatexis in the Mount Painter province, South Australia: timing, thermal budgets and the role of crustal heat production, Journal of Petrology, 47, 2281-2302  doi:10.1093/petrology/egl044 
`r margin_note(  gs("Palaeozoic intraplate crustal anatexis"))` 
1.	Quigley, M., Yu Liangjun, Liu Xiaohan, Wilson, C.J.L, __Sandiford, M.__, Phillips, D., 2006, 40Ar/39Ar thermochronology of the Kampa Dome, southern Tibet: implications for the thermal evolution of North Himalayan middle crust, Tectonophysics, 421, 269-297 
`r margin_note( gs("thermochronology of the Kampa Dome"))`
1.	Nelson, E., Hillis, R., __Sandiford, M.__, Reynolds, S., Lyon, P., Meyer, J., Mildren, S., Rogers, C., 2006, Present-day state-of-stress of southeast Australia, APPEA Journal 2006, 283-305 
1.	Grew, E.S., Yates, M.G.,Shearer, C.K., Hagerty, J.J., Sheraton, J.W., __Sandiford, M.__, 2006, Beryllium and other trace elements in paragneisses and anatectic veins of the ultrahigh-temperature Napier Complex, Enderby Land, East Antarctica: the role of sapphirine, Journal of Petrology, 47, 859-882  doi:10:1093/petrology/egi098 
`r margin_note(  gs("Beryllium and other trace elements in paragneisses and anatectic"))` 
1.	__Sandiford, M.__, McLaren, S., 2006, Thermo-mechanical controls on heat production distributions and the long-term evolution of the continents, "Evolution and differentiation of the continental crust" (eds, Brown, M. and Rushmer, T.), Cambridge University Press, 67-91 
`r margin_note(  gs("Thermo-mechanical controls on heat production"))
` 
1.	Quigley, M., Cupper, M., __Sandiford, M.__, 2006, Quaternary faults of south-central Australia: palaeoseismicity, slip rates and origin, Australian Journal of Earth Sciences, 53, 285-301 
`r margin_note(  gs( "Quaternary faults of south-central Australia"))`
1.	Bodorkos, S., __Sandiford, M.__, 2006, Thermal and mechanical controls on the evolution of Archean crustal deformation: examples from Western Australia, AGU Volume Archean Geodynamic and Environments, (eds, Keith Benn, Jean-Cl\\$e Mareschal, Kent Condie). Geophysical Monograph Series 164, American Geophysical Union), 370 
`r margin_note(  gs("Thermal and mechanical controls on the evolution of Archean crustal"))`
1.	__Sandiford, M.__, Hansen D.L., McLaren, S.N., 2006, Lower crustal rheological expression in inverted basins, in Analogue and Numerical Modelling of Crustal Scale Processes (eds Buiter, S. and Schreurs, G.). Geological Society Special Publication, 253, 271-283 
`r margin_note(  gs("lower crust rheological"))
` 
1.	Celerier, J., __Sandiford, M.__, Hansen, D.L., Quigley, M., 2005, Modes of active intraplate deformation, Flinders Ranges, Australia, Tectonics, 24  doi:10.029/2004andC001679 
`r margin_note(  gs("Modes of active intraplate deformation"))`
1.	McLaren, S., __Sandiford, M.__, Powell, R., 2005, Contrasting styles of Proterozoic crustal evolution: a hot-plate tectonic model for Australian terranes, Geology, 33,673-676 
`r margin_note(  gs("Contrasting styles of Proterozoic crustal evolution"))
`
1.	Wallace, M., Dickinson, J.A., Moore, D., __Sandiford, M.__, 2005, Late Neogene strandlines of Southern Victoria: A unique record of eustasy and tectonics in southeast Australia, Australian Journal of Earth Sciences, 52, 277-295.
`r margin_note(  gs("Late Neogene strandlines"))
`
1.	de Broekert, P., __Sandiford, M.__, 2005, Buried inset-valleys in the eastern Yilgarn Craton, Western Australia: Geomorphology, age and allogenic control, Journal of Geology, 113, 471-493
`r margin_note(     gs("Buried inset‐valleys in the eastern Yilgarn Craton, Western Australia: Geomorphology, age, and allogenic control"))
`
1.	__Sandiford, M.__, Coblentz, D., Schellart, W.P., 2005, Evaluating slab-plate coupling in the Indo-Australian plate, Geology, 33, 113-116
`r margin_note( gs("Evaluating slab-plate coupling"))
`
1.	__Sandiford, M.__, Wallace, M., Coblentz, D, 2004, Origin of the in situ stress field in south-eastern Australia, Basin Research, 16, 325-338
`r margin_note(  gs("in situ stress field in south-eastern Australia"))
`
1.	__Sandiford, M.__, Van Kranendonk, M., Bodorkos, S., 2004, Conductive incubation and the origin of granite-greenstone dome and keel structure: the Eastern Pilbara Craton, Australia, Tectonics, 23, TC1009, doi: 10.1029/2002TC001452 
`r margin_note(  gs( "Conductive incubation"))
`
1.	Bodorkos, S., __Sandiford, M.__, Minty, B.R.S., Blewett, R.S., 2004, A high-resolution, calibrated airborne radiometric dataset applied to the estimation of crustal heat production in the Archaean northern Pilbara Craton, Western Australia, Precambrian Research, 128, 57-82
`r margin_note(  gs("calibrated radiometric"))
` 
1.	__Sandiford, M.__, Leonard, M., Coblentz, D, 2003, Geological constraints on active seismicity in southeast Australia, In "Earthquake Risk Mitigation", (eds, Wilson, J.L, Lam, N.K., Gibson. G.), Australian Earthquake Engineering Society, 1-10
1.	__Sandiford, M.__, Frederiksen, S., Braun, J., 2003, The long-term thermal consequences of rifting: implications for basin reactivation, Basin Research,15, 23-43
`r margin_note(  gs("thermal consequences of rifting"))
` 
1.	__Sandiford, M.__, 2003, Geomorphic constraints on the late Neogene tectonics of the Otway Range, Victoria, Australian Journal of Earth Sciences, 50, 69-80
`r margin_note(  gs("Geomorphic constraints on the Late Neogene tectonics of the Otway Range, Victoria"))
`
1.	McLaren, S., __Sandiford, M.__, Hand, M., Neumann, N., Wyborn, L., Bastrakova, I., 2003, The hot southern continent, Heat flow and heat production in Australian Proterozoic terranes, eds Hillis, R.R. Muller, D., Evolution and dynamics of the Australian Plate, Geological Society of Australia, Special Publication, 22, 151-161
`r margin_note( gs("The hot southern continent"))
`
1.	__Sandiford, M.__, 2003, Neotectonics of southeastern Australia: linking the Quaternary faulting record with seismicity and in situ stress, eds Hillis, R.R. Muller, D., Evolution and dynamics of the Australian Plate, Geological Society of Australia, Special Publication, 22, 101-113
`r margin_note( gs( "Neotectonics of southeastern Australia"))
` 
1.	__Sandiford, M.__, 2002, Late Neogene faulting record in southeastern Australia, In Victoria Undercover, (eds. Phillips, G.N., and Ely, K.S.,), 131-135
1.	__Sandiford, M.__, McLaren, S., 2002, Tectonic feedback and the ordering of heat producing elements within the continental lithosphere, Earth and Planetary Science Letters, 2002, 204, 133-150
`r margin_note(  gs("Tectonic feedback and the ordering of heat producing"))
` 
1.	__Sandiford, M.__,2002, Low thermal Peclet number intraplate orogeny in central Australia, Earth and Planetary Science Letters,201, 309-320.
`r margin_note(  gs("Peclet number"))
` 
1.	Foden, J.D., Elburg, M.A., Turner, S.P., __Sandiford, M.__, O'Callghan, J., Mitchell, S., 2002, Granite production in the Delamerian Orogen, South Australia, Journal of the Geological society of London, 159, 557-575
`r margin_note(  gs("Granite production in the Delamerian orogen, South Australia"))
` 
1.	McLaren, S., Dunlap, J., __Sandiford, M.__ McDougall, I., 2002, The thermochronology of high heat-producing crust at Mount Painter, South Australia: implications for tectonic reactivation of continental interiors, Tectonics doi:10.1029/2000TC001275 
`r margin_note(  gs("crust at Mount Painter"))
` 
1.	Alías, G., __Sandiford, M.__, Hand, M., Worley, B., 2002, The P-T record of synchronous magmatism, metamorphism and deformation at Petrel Cove, southern Adelaide Fold Belt, Journal of Metamorphic Geology, 20, 351-36 
`r margin_note( gs("Petrel Cove"))
` 
1.	Bodorkos, S., __Sandiford, M.__, Oliver, N.H.S., Cawood, P.A. 2002, High-T, low-P metamorphism as the middle crustal response to a mantle-related transient thermal pulse: a numerical model and its application to the Palaeoproterozoic Halls Creek Orogen, northern Australia, Journal of Metamorphic Geology, 20, 217-237
`r margin_note( gs("Halls Creek"))
` 
1.	__Sandiford, M.__, McLaren, S., Neumann, N, 2002, Long-term thermal consequences of the redistribution of heat-producing elements associated with large-scale granitic complexes, Journal of Metamorphic Geology, 20, 87-98
`r margin_note( gs("consequences of the redistribution"))
` 
1.	Haines, P, Hand, M., __Sandiford, M.__, 2001, Palaeozoic syn-orogenic sedimentation in central and northern Australia: a review of distribution and timing with implications for the evolution of intracontinental orogens, Australian Journal of Earth Sciences, 48, 911-928
`r margin_note(  gs("Palaeozoic synorogenic sedimentation in central and northern Australia"))
` 
1.	__Sandiford, M.__, Hand, M.,McLaren, S., 2001, Tectonic feedback, intraplate orogeny and the geochemical structure of the crust: a central Australian perspective, In Continental Reactivation and Reworking, (eds, Miller, J., Holdsworth, R., Buick, I., Hand, M.), Geological Society Special Publication No. 184, 195-218
`r margin_note(  gs("Tectonic feedback, intraplate orogeny and the geochemical structure"))
`
1.	McLaren, S., __Sandiford, M.__, 2001, Long-term thermal consequences of tetconic activity at Mount Isa, Australia: Implications for polyphase tectonism in the Proterozoic.In Continental Reactivation and Reworking, (eds, Miller, J., Holdsworth, R., Buick, I., Hand, M.), Geological Society Special Publication No. 184, 219-236
`r margin_note(  gs("implications for polyphase tectonism"))
` 
1.	Neumann, N, __Sandiford, M.__, Foden, J., 2000, Regional geochemistry and continental heat flow: Implications for the origin of the South Australian heat flow anomaly. Earth and Planetary Science Letters, 183, 107-120
`r margin_note(  gs("Regional geochemistry and continental heat flow"))
` 
1.	Fraser, G., Worley, B., __Sandiford, M.__, 2000, High‐precision geothermobarometry across the High Himalayan metamorphic sequence, Langtang Valley, Nepal. Journal of metamorphic Geology,18, 665 - 682
`r margin_note(  gs("High‐precision geothermobarometry across the High Himalayan metamorphic sequence"))
` 
1.	McLaren, S., __Sandiford, M.__, Hand, M., 2000, High radiogenic heat producing granites and metamorphism - an example from the western Mount Isa Inlier, Australia, reply to comment, Geology, 28, 672
`r margin_note(  gs( "western Mount Isa Inlier"))
` 
1.	Paul, E., __Sandiford, M.__, Flottman, T., 2000, The structural geometry of a thick-skinned fold-thrust belt termination : the Olary Block in the Adelaide Fold Belt, South Australia. Australian Journal of Earth Sciences, 47, 281-290
`r margin_note(  gs( "Olary"))
` 
1.	Arnold, J., Powell, R., __Sandiford, M.__, 2000, Amphibolites with staurolite and other aluminous minerals: calculated mineral equilibria in NCFMASH, Journal of metamorphic Geology, 18, 23-40  `r margin_note(  gs( "NCFMASH"))` 
1.	McLaren, S., __Sandiford, M.__, Hand, M., 1999, High radiogenic heat producing granites and metamorphism - an example from the western Mount Isa Inlier, Australia, Geology, 27, 679-682
`r margin_note(  gs( "western Mount Isa Inlier"))
` 
1.	Hand, M., __Sandiford, M.__, Wyborn, L., 1999, Some thermal consequences of high heat production in the Australian Proterozoic. AGSO research Newsletter, 30, 20-23 `r margin_note(  gs( "Some thermal consequences of high heat production in the Australian Proterozoic"))` 
1.	McLaren, S., Neumman, N., __Sandiford, M.__, Wyborn, L., 1999, Post-intrusion heating associated with high-heat-producing Proterozoic granites - Implications for mineralisation? AGSO research Newsletter, 30, 23-26
`r margin_note(  gs( "Post-intrusion heating"))` 
1.	Tokarev, V., __Sandiford, M.__, Gostin, V., 1999, Landscape evolution in the Mount Lofty Ranges: implications for regolith development. In Regolith'98 : new approaches to an old continent, (eds) Taylor, G., Pain C., 131-139.
`r margin_note(  gs( "regolith development"))` 
1.	Hand, M., __Sandiford, M.__, 1999, Intraplate deformation in central Australia, the link between subsidence and fault ractivation, Tectonophysics, 305, 121-140
`r margin_note(  gs( "Intraplate deformation in central Australia, the link between subsidence and fault reactivation"))` 
1.	__Sandiford, M.__, 1999, Mechanics of basin inversion, Tectonophysics, 305, 109-120
`r margin_note( gs("Mechanics of basin inversion"))` 
1. Paul, E., Flottmann, T., __Sandiford, M.__, 1999, Structural geometry and controls on basement-involved deformation in  the northern Flinders Ranges, Adelaide Fold Belt, South Australia, Australian Journal of Earth Sciences, 46, 343-354
`r margin_note(  gs("Structural geometry and controls on basement‐involved deformation in the northern Flinders Ranges, Adelaide Fold Belt, South Australia"))` 
1.	Foden, J., __Sandiford, M.__, Dougherty-Page, J., Willliams, I., 1999, Geochemistry and geochronology of the Rathjen Gneiss: implications for the early tectonic evolution of the Delamerian Orogen. Australian Journal of Earth Science, 46, 377-389
`r margin_note(  gs("Geochemistry and geochronology of the Rathjen Gneiss"))` 
1.	__Sandiford, M.__, Paul, E., Flottmann, T., 1998, Sedimentary thickness variations and deformation intensity during basin inversion in the Flinders Ranges, South Australia, Journal of Structural Geology, 20, 1721-1731
`r margin_note( gs( "Sedimentary thickness variations and deformation"))` 
1.	__Sandiford, M.__, Hand, M., McLaren, S., 1998, High geothermal gradient metamorphism during thermal subsidence, Earth and Planetary Science Letters, 163, 149-165
`r margin_note(  gs("High geothermal gradient metamorphism"))` 
1.	__Sandiford, M.__, Hand, M., 1998, Controls on the locus of Phanerozoic intraplate deformation in central Australia, Earth and Planetary Science Letters, 162, 97-110
`r margin_note(  gs( "Controls on the locus of"))` 
1.	Coblentz, D., Zhou, S., Hillis, R., Richardson, R., __Sandiford, M.__, 1988, Topography, plate-boundary forces and the Indo-Australian intraplate stress field, Journal of Geophysical Research, 103, 919-931
`r margin_note(  gs("boundary forces, and the Indo-Australian intraplate stress field"))` 
1.	__Sandiford, M.__, Hand, M., 1998, Australian Proterozoic high-temperature metamorphism in the conductive limit, In What Controls Metamorphism, (ed) Treloar, P., and O’Brien, P, Geological Society of London Special Publication, 138, 103-11 `r margin_note(  gs( "Australian Proterozoic high-temperature"))` 
1.	Hillis, R., __Sandiford, M.__, Coblentz, D., Zhou, S., 1997, Modelling the Contemporary stress field and its implications for Hydrocarbon exploration, Exploration Geophysics, 28, 88-93  `r margin_note(  gs( "Hydrocarbon exploration"))` 
1.	Turner, S., Kelly, S.P, Vandenberg, A.H., Foden, J., __Sandiford, M.__, Flotmmann, T., 1996, Source of Delamerian fold belt flysch linkes to convective removal of the lithospheric mantle and rapid exhumation of the Delamerian-Ross fold belt, Geology, 24, 941-944  `r margin_note(  gs( "Ross fold belt"))` 
1.	Zhou, S., Hillis, R , __Sandiford, M.__, 1996, A supplement to 'A study of inclined wellbores with regard to both mechanical stability and fracture intersection and its application to the Australian North West Shelf', Journal of Applied Geophysics, 36, 145-147.`r margin_note(  gs( "A supplement to"))` 
1.	Zhou, S., Hillis, R , __Sandiford, M.__, On the mechanical stability of inclined boreholes, SPE drilling, 11, 67-73. `r margin_note(  gs( "On the mechanical stability of"))` 
1.	Turner, S., __Sandiford, M.__, Flottman, T., Foden, J., 1995, Rb/Sr dating of differentiated cleavage from the Adelaidean metasediments at Hallet Cove, southern Adelaide Fold Belt: Reply to disucssion by W.V. Preiss, Journal of Structural Geology, 17, 1801-1803.  
1.	Arnold, J., __Sandiford, M.__, Wetherley, S., 1995, Metamorphic events in the Eastern Arunta Inlier, Part 1. Metamorphic petrology, Precambrian Research,71, 183-205.  `r margin_note(  gs( "Eastern Arunta Inlier"))` 
1.	Coblentz, D., __Sandiford, M.__, Richardson, R, Zhou, S., Hillis, R., 1995, The origins of the Australian stress field, Earth and Planetary Science Letters, 133, 299-309. `r margin_note(  gs( "The origins of the intraplate stress field in continental Australia"))` 
1.	__Sandiford, M.__, Coblentz, D., Richardson, R.M., 1995, Ridge torques and continental collision in the Indian-Australian plate, Geology, 23, 653-656. `r margin_note(  gs( "Ridge torques and continental collision in the Indian-Australian plate"))` 
1.	Stuwe, K., __Sandiford, M.__, 1995, Description of Metamorphic Pressure- Temperature-Time paths in the Low-P High-T Environment, Physics of the Earth and Planetary Interiors, 88, 211-221. `r margin_note(  gs( "Description of Metamorphic Pressure"))` 
1.	Stuwe, K., __Sandiford, M.__, 1995, Mantle lithospheric deformation and crustal metamorphism, with some speculations on the thermal and mechanical significance of the Tauern event, Eastern Alps, Tectonophysics, 214, 115-132. `r margin_note(  gs( "lithospheric deformation and crustal metamorphism"))` 
1.	__Sandiford, M.__, Fraser, G., Arnold, J., Foden, J., Farrow, T., 1995, Some causes and consequences of high‐temperature, low‐pressure metamorphism in the eastern Mt Lofty Ranges, South Australia, Australian Journal of Earth Sciences, 42, 233-240.`r margin_note(  gs( "Some causes and consequences of high‐temperature, low‐pressure metamorphism in the eastern Mt Lofty Ranges, South Australia"))` 
1.	Mildren, S., __Sandiford, M.__, 1995, A heat refraction mechanism for Low-P metamorphism in the northern Flinders Ranges, South Australia, Australian Journal of Earth Sciences, 42, 241-247. `r margin_note(  gs( "heat refraction"))` 
1.	Cartwright, I., Vry, J., __Sandiford, M.__, 1995, Changes in stable isotope ratios of metapelites and marbles during regional metamorphism, Mount Lofty Ranges, South Australia: Implications for crustal scale fluid flow, Contributions to Mineralogy and Petrology, 120, 292-310. `r margin_note(  gs( "Changes in stable isotope ratios of metapelites"))` 
1.	Zhou, S., Hillis, R., __Sandiford, M.__, 1994, A study of inclined wellbores with regard to both mechanical stability and fracture intersection and its application to the Australian North West Shelf, Journal of Applied Geophysics, 32, 293-304.`r margin_note(  gs( "inclined wellbores"))` 
1.	Coblentz, D., __Sandiford, M.__, 1994, Tectonic stresses in the African plate: Constraints on the ambient stress state, Geology, 22, 831-834. `r margin_note(  gs( "Tectonic stresses in the African plate"))` 
1.	Coblentz, D., Richardson, R.M., __Sandiford, M.__, 1994, On the gravitational potential of the Earth's lithosphere, Tectonics, 13, 929-945. `r margin_note(  gs( "On the gravitational potential of "))` 
1.	Ehlers, K., Stuwe, K., Powell, R., __Sandiford, M.__, Frank, W., 1994, Thermometrically inferred cooling rates from the Plattengneis, Koralm Region - Eastern Alps, Earth and Planetary Science Letters, 125, 307-321.`r margin_note(  gs( "inferred cooling rates from the"))` 
1.	__Sandiford, M.__, Coblentz, D., 1994, Plate-scale potential energy distributions and the fragmentation of ageing plates, Earth and Planetary Science Letters, 126, 143-159. `r margin_note(  gs( "fragmentation"))` 
1.	Stuwe, K., __Sandiford, M.__, 1994, A possible contribution of deviatoric stresses to metamorphic PT paths; an example appropriate to low-P, high-T metamorphism, Journal of Metamorphic Geology, 12, 445-454. `r margin_note(  gs( "deviatoric stresses to metamorphic"))` 
1.	Turner, S., __Sandiford, M.__, Flottman, T., Foden, J., 1994, Rb-Sr dating of differentiated cleavage: an example from the Adelaidean metasediments at Hallet Cove, with implications for the tectonic evolution of the southern Adelaide Fold Belt, Journal of Structural Geology, 16, 1233-1242. `r margin_note(  gs( "differentiated cleavage"))` 
1.	Stuwe, K., __Sandiford, M.__, 1994, Some remarks on the geomorphological evolution of the eastern Alps, constraints on Cretaceous nappe tectonics, Mitteilungen der Osterreichischen geologischen Gesellschaft, 86, 165-176.
`r margin_note(  gs( "evolution of the eastern Alps"))` 
1.	Stuwe, K., __Sandiford, M.__, 1993, A preliminary model for the 500 Ma event in the East Antarctic Shield, In: Gondwana Eight (eds. Findlay, Unrug and Veevers), Balkema, 125, `r margin_note(  gs( "500 Ma"))` 
1.	Turner, S., Foden, J., __Sandiford, M.__, Bruce, D., 1993, Sm-Nd isotopic evidence for the provenance of sediments from the Adelaide Fold Belt and southeastern Australia with implications for crustal growth models, Geochemica Cosmochemica Acta, 57, 1837-1856. `r margin_note(  gs( "provenance of sediments from the Adelaide Fold Belt"))` 
1.	Stuwe, K., __Sandiford, M.__, Powell, R., 1993, Episodic metamorphism and deformation events in Low-P, High-T terrains, Geology, 21, 829-832. `r margin_note(  gs("Episodic metamorphism"))` 
1.	Scrimgeour, I., __Sandiford, M.__, 1993, Early Proterozoic metamorphism at the Granites, northern Territory, implications for fluid production in high T - low P terrains, Economic Geology, 88, 1099-1113.
`r margin_note(  gs( "metamorphism at the Granites")) ` 
1.	Dymoke, P., __Sandiford, M.__, 1992, Phase relations in Buchan facies series pelitic assemblages: calculations with application to andalusite-staurolite assemblages in the Mount Lofty Ranges, South Australia, Contributions to Mineralogy and Petrology, 110, 121-132. `r margin_note(  gs( "Phase relationships in Buchan facies series pelitic assemblages")) ` 
1.	Jenkins, R.F.J., __Sandiford, M.__, 1992, Observations on the tectonic evolution of the southern Adelaide fold Belt, Tectonophysics, 214, 27-36. `r margin_note( gs( "Observations on the tectonic evolution"))` 
1.	__Sandiford, M.__, Foden, J., Zhou, S., Turner, S., 1992, Granite genesis and the mechanics of convergent orogenic belts with application to the southern Adelaide Fold Belt. Proceedings of the Royal Society of Edinburgh (Hutton Symposium Volume) 83, 83-93. `r margin_note(  gs( "Granite genesis and the mechanics"))` 
1.	Zhou, S., __Sandiford, M.__, 1992, On the stability of isostatically compensated mountain belts. Journal of Geophysical Research, 97, 14207-14221. `r margin_note(  gs("On the stability of isostatically compensated"))` 
1.	__Sandiford, M.__, Foden, J., Zhou, S., Turner, S., 1992, Granite genesis and the mechanics on convergent orogenic belts with application to the southern Adelaide Fold Belt. Geological Society of America, Special Paper, 273, 83-93.`r margin_note(  gs("Granite genesis and the mechanics"))`
1.	Turner, S., __Sandiford, M.__, Foden, J., 1992, Some geodynamic and compositional constraints on "post-orogenic" magmatism, Geology, 20, 931-934. `r margin_note( gs("Some geodynamic and compositional constraints"))` 
1.	Ding, P., James, P., __Sandiford, M.__, 1992, Late Proterozoic deformation in the Amadeus Basin, central Australia. Australian Journal of Earth Sciences, 39, 495-500. `r margin_note(  gs("Late Proterozoic deformation in the Amadeus Basin"))`
1.	__Sandiford, M.__, Santosh, M., 1991, A granulite facies kalsilite-leucite-hibonite association from Punalur, southern India. Mineralogy and Petrology, 43, 225-236.`r margin_note(  gs("kalsilite"))`
1.	__Sandiford, M.__, Dymoke, P., 1991, Some remarks on the stability of blueschists and related high P - low T assemblages in continental orogens, Earth and Planetary Science Letters, 102, 14-23. `r margin_note(  gs("stability of blueschists"))`
1.	__Sandiford, M.__, Powell, R., 1991, Some remarks on high temperature-low pressure metamorphism in convergent orogens, Journal of Metamorphic geology, 9, 333-340. `r margin_note(  gs( "metamorphism in convergent orogens"))` 
1.	Santosh, M., __Sandiford, M.__, Reed, S.J.B., 1991, Zoned hibonites from Punalur, South India, Mineralogical Magazine, 55, 159-162.  `r margin_note(  gs("Zoned hibonites"))`
1.	__Sandiford, M.__, Martin, N., Zhou, S., Fraser, G., 1991, Mechanical consequences of granite emplacement during high-T, low-P metamorphism and the origin of "anticlockwise" PT paths, Earth and Planetary Science Letters, 107, 164-172. `r margin_note(  gs("Mechanical consequences of granite"))`
1.	__Sandiford, M.__, Oliver, R.L., Mills, K.J., Allen, R.V., 1990, A cordierite-staurolite- muscovite association east of Springton, Mount Lofty Ranges; implications for the metamorphic evolution of the Kanmantoo Group. In "Proterozoic and early Palaeozoic geology of the Adelaide Geosyncline", Geological Society of Australia, Special publication (Daily Volume), 16, 483-495.`r margin_note(  gs("muscovite association"))`
1.	__Sandiford, M.__, Powell, R., 1990, Some thermal and isostatic consequences of the vertical strain geometry in convergent orogens, Earth and Planetary Science Letters, 98, 154 - 165. `r margin_note(  gs( "vertical strain geometry"))` 
1.	Arnold, J., __Sandiford, M.__, 1990, Petrogenesis of cordierite-orthoamphibole assemblages in the Springton region, South Australia, Contributions to Mineralogy and Petrology, 106, 100-109. `r margin_note(  gs("Springton region"))`
1.	__Sandiford, M.__, 1989, Horizontal structures in granulite terrains : a record of mountain building or mountain collapse? Geology, 17, 449 - 452. `r margin_note(  gs( "Horizontal structures in granulite terrains"))` 
1.	__Sandiford, M.__, 1989, Secular trends in the thermal evolution of metamorphic belts, Earth and Planetary Science Letters, 95, 85-96. `r margin_note(  gs("secular trends"))`
1.	Powell, R., __Sandiford, M.__, 1988, Sapphirine and spinel phase relationships in the system FeO-MgO-SiO2-TiO2-Al2O3-O2 in the presence of quartz and hypersthene. Contributions to Mineralogy and Petrology, 98, 64-71.`r margin_note(  gs("Sapphirine and spinel phase relationships"))`
1.	Waldron, W., __Sandiford, M.__, 1988, Deformation volume and cleavage development in metasediments from the Ballarat Slate Belt, Journal of Structural Geology, 10, 53-62.`r margin_note(  gs("Deformation volume and cleavage development"))`
1.	__Sandiford, M.__, Powell, R., Martin, S.F., Perera, L.R.K., 1988. Thermal and baric evolution of garnet granulites, Sri Lanka. Journal of Metamorphic Geology, 6, 351-364.`r margin_note(  gs("Sri Lanka"))`
1.	__Sandiford, M.__, Powell, R., 1988, Pyroxene exsolution in granulites from Fyfe Hills, Enderby Land, Antarctica; evidence for 1000°C metamorphic temperatures in Archaean continental crust; reply. American Mineralogist, 73, 434-438.
1.	__Sandiford, M.__, Martin, S.F., Lowe, E., 1988, Shear zone deformation in the Yackandandah granite, NE Victoria, Australian Journal of Earth Science, 35, 223-230. `r margin_note(  gs("Yackandandah"))`
1.	Fitzgerald, P.F., __Sandiford, M.__, Barret, P.J., Gleadow, A.J.W., 1987, Asymmetric extension associated with uplift and subsidence in the Transantarctic Mountains and Ross Embayment, Earth and Planetary Science Letters, 81, 67-78. `r margin_note(  gs("Asymmetric extension associated with uplift"))` 
1.	__Sandiford, M.__, Neall, F., Powell, R., 1987, Metamorphic evolution of granulites from Labwor Hills, Uganda, Contributions to Mineralogy and Petrology, 95, 217-225.
`r margin_note(  gs("Labwor Hills"))` 
1.	Baker, J., Powell, R., __Sandiford, M.__, Muhling, J., 1987, Corona textures between kyanite, garnet and gedrite gneisses from Errabiddy, Western Australia. Journal of Metamorphic Geology, 5, 557-570.
`r margin_note(  gs("textures between kyanite"))` 
1.	__Sandiford, M.__, Wilson, C., 1986, The origin of Archaean gneisses in the Fyfe Hills region, Enderby Land, Antarctica; field occurrence, petrography and geochemistry, Precambrian Research, 31, 37-68.
`r margin_note(  gs("The origin of Archaean gneisses"))`  
1.	__Sandiford, M.__, Powell, R., 1986, Pyroxene exsolution in granulites from Fyfe Hills, Enderby Land, Antarctica: evidence for 1000°C metamorphic temperatures in Archaean continental crust, American Mineralogist, 71, 946-954. `r margin_note(  gs("exsolution in granulites"))`  
1.	__Sandiford, M.__, Powell, R., 1986, Deep crustal metamorphism during continental extension, ancient and modern examples. Earth and Planetary Science Letters, 79, 151-158. `r margin_note(  gs("Deep crustal metamorphism during continental extension"))`  
1.	__Sandiford, M.__, Keays, R., 1986, Structural and tectonic constraints on the origin of gold in the Ballarat Slate Belt, in Kleppie, J.D. (Ed.) "Turbidite hosted gold deposits", Geological Society of Canada, Special paper, 32,15-24. `r margin_note(  gs("Ballarat Slate Belt"))`  
1.	__Sandiford, M.__, 1985, The metamorphic evolution of granulites from Fyfe Hills, implications for Archaean crustal thickness in Enderby Land, Antarctica. Journal of Metamorphic Geology, 3, 155-178. `r margin_note(  gs("crustal thickness in Enderby Land"))`  
1.	__Sandiford, M.__, 1985, The structural evolution of the Lanterman metamorphic complex, northern Victoria Land, New Zealand Journal of Geology and Geophysics, 28, 443-458.  
`r margin_note(  gs("Lanterman metamorphic complex"))`  

1.	__Sandiford, M.__, 1985, The origin of retrograde shear zones in the Napier Complex, implications for the tectonic evolution of Enderby Land, Antarctica, Journal of Structural Geology, 7, 477-488.
`r margin_note(  gs("retrograde shear zones"))`  
1.	Grew, E.S., __Sandiford, M.__, 1985, Staurolite in a garnet-hornblende-biotite schist from the Lanterman Range, northern Victoria Land, Antarctica, Neues Jarbuch Mineralogie, Heft, 9, 396-410.
`r margin_note(  gs("Staurolite in a garnet–hornblende–biotite schist from the Lanterman Range"))`  
1.	__Sandiford, M.__, Wilson, C.J.L., 1984, The structural evolution of the Fyfe Hills - Khmara Bay region, Enderby Land, East Antarctica, Australian Journal of Earth Sciences, 31, 403- 426. `r margin_note(  gs("Khmara Bay"))` 
1.	Grew, E.S., __Sandiford, M.__, 1984, A staurolite-talc assemblage in tourmaline-phlogopite- chlorite schist from Northern Victoria Land, Antarctica and its petrogenetic significance. Contributions to Mineralogy and Petrology, 87, 337-350. `r margin_note(gs("A staurolite-talc assemblage in tourmaline-phlogopite-chlorite schist"))`  
1.	Grew, E.S., Manton, W.I., __Sandiford, M.__, 1983, Geochronologic studies in East Antarctica: age of pegmatites in Casey Bay, Enderby Land. Antarctic Journal of the United States, 17, 1-2. `r margin_note(  gs("Casey"))` 
1.	Grew, E.S., __Sandiford, M.__, 1983, Field studies of the Wilson and Rennick Groups, Rennick Glacier area, northern Victoria Land. Antarctic Journal of the United States, 17, 7-8. `r margin_note(  gs("Rennick"))` 
1.	__Sandiford, M.__, Wilson, C.J.L. 1983, The Geology of the Fyfe Hills- Khmara Bay Region, Enderby Land, in Oliver, R.L., James, P.R. and Jago, J.B. Antarctic earth sciences, Australian Academy of Sciences, Canberra, 16-19
`r margin_note(  gs("The Geology of the Fyfe Hills"))`  


## 5.2 Non refereed papers, commissioned reports and working papers

1. McConnell, D. \&  __Sandiford, M.__, 2016,  Winds of Change - an analysis of recent changes in the South Australian Electricity Market, Melbourne Energy Institute
  commissioned by Australian Conservation Foundation, p.55.
  ```{marginfigure} 
  [link](http://energy.unimelb.edu.au/__data/assets/pdf_file/0017/2054132/SA_PRICES_FINAL.pdf)
  ```
1. Lafleur, D., Forcey, T., Saddler, H. \& __Sandiford, M.__, 2016, A review of current and future methane emissions from Australian unconventional oil and gas production,
   Melbourne Energy Institute, commissioned by  The Australia Institute, p.96.
   ```{marginfigure} 
   [link](http://www.tai.org.au/sites/defualt/files/MEI%20Review%20of%20Methane%20Emissions%20-%2026%20October%202016.pdf)
   ```
1.  Lafleur, D., __Sandiford,M.__, 2016, The risk of migratory emissions from Coal seam gas developments in Queensland, Melbourne Energy Institute,  The Australia Institute
1. M Sandiford, M Watt, A Vasallo, 2016, Energy for Australia in the 21st Century: The central role of electricity, Australian Academy of Sciences, Future Science, p.56
 ```{marginfigure} 
 [link](https://www.science.org.au/files/userfiles/support/reports-and-plans/2016/future-science-energy-report.pdf)
 ```
1.  Beardsmore, G.,  Dumitrescu, I.,  Harrison, B., __Sandiford, M.__ \&  Webster, R.,  2016, Victorian Geothermal Assessment Report, Melbourne Energy Institute, p. 62, 
```{marginfigure} 
[link](http://energy.unimelb.edu.au/__data/assets/pdf_file/0007/2170528/mel036-Victorian-Geothermal-Assessment-Report-2015-WEB1.pdf)
```
1.   Hoffman, N.,  Hardman-Mountford, N., Jenkins, C., Rayner,  P .,  Gibson, G. \& __Sandiford, M.__, 2016, GipNet – Baseline environmental data gathering and measurement technology validation for nearshore marine Carbon Storage,  CarbonNet, published by Global CCS Institute, p 37.
 ```{marginfigure} 
 [link](http://hub.globalccsinstitute.com/sites/default/files/publications/200408/GipNet%20Environmental%20Baseline%20Studies.pdf)
 ```
1. Howard, W., __Sandiford,M.,__ Elliot, S., Talberg, A., Lafleur, D.,  Bice, S. \& Rawling, T., 2014, The sedimentary Basin Management Initiative,  Melbourne Energy Institute
  commissioned by Carlton Connect, University of Melbourne, p 26. 
  ```{marginfigure} 
  [link](url: https://www.carltonconnect.com.au/wp-content/uploads/2016/01/SBMI-Position-Analysis.pdf)
  ```
1. Hearps, P., Dargaville,R.,  McConnell, D., __Sandiford, M.,__ Forcey, T. \&  Seligman, P., 2014, Opportunities for Pumped Hydro Energy Storage in Australia, Melbourne Energy Institute
  commissioned by ARUP, p.96.
```{marginfigure} 
[link](http://energy.unimelb.edu.au/__data/assets/pdf_file/0007/1526587/Opps-for-pumped-hydro-in-Australia.pdf)
```
1.  Forcey, T. \&  __Sandiford,M.__ 2015, The dash from gas. Could demand in New South Wales fall to half?, Melbourne Energy Institute
  commissioned by The Australia Institute, p.30 
  ```{marginfigure} 
  [link](http://www.tai.org.au/sites/defualt/files/MEI%20Report%20-%20Dash%20From%20Gas.pdf)
  ```
1. Exploration whitepaper, IPGT, 2012 
```{marginfigure} 
[link](http://internationalgeothermal.org/Working_Groups/Documents/FINAL%20Exploration%20Working%20Group%20Whitepaper%20August%202012.pdf)
```
1. Multi basin usage/cumulative impacts, Rawling T. \& __Sandiford, M.__, p. 38, NSW Chief Scientist CSG Review, 2014 
```{marginfigure} 
[link](http://www.chiefscientist.nsw.gov.au/__data/assets/pdf_file/0015/31614/Multi-basin-usage-and-cumulative-impact-background-paper_Rawling-and-Sandiford.pdf)
```
1.  Seismicity and induced earthquakes, Gibson, G. \& __Sandiford, M.__, p. 33, NSW Chief Scientist CSG Review, 2014
```{marginfigure} 
[link](http://www.chiefscientist.nsw.gov.au/__data/assets/pdf_file/0017/31616/Seismicity-and-induced-earthquakes_Gibson-and-Sandiford.pdf)
```
1. Soares, S., Mills, C., Sandiford, M. \& dos Reis, J., 2011,Landslide occurrence in East Timor, Melbourne Energy Institute Technical paper series,  38 pp.
1.  McConnell, D.  Hearps, P. \& Sandiford, M., 2011, Solar PV in Australia,  Melbourne Energy Institute,
  commissioned by TruEnergy
1. M Sandiford and others, 2011, The Australian Earth Observatory – infrastructure roadmap, AuScope
  commissioner: AuScope
  ```{marginfigure} 
  [link](http://www.auscope.org.au/wp-content/uploads/2015/11/AEO_AuScope_Nov_2011.pdf)
  ```
1.	__Sandiford, M.__, 2010, Victoria's unique geothermal option, Victorian supplement 2010-Victoria's Energy Resources, 12-13.
1.	__Sandiford, M.__, 2010, A slow divorce: tectonic signals in an ancient continent, The Australian Geologist, 157, 29-31.



## 5.3 Geological Maps and datasets
* 1:50,000 Geological Map Sheet, Atauro, Timor Leste, 2005
* 1:50,000 Geological Map Sheet, Dili, Timor Leste, 2012
* 1:50,000 Geological Map Sheet, Laclo, Timor Leste, 2014
* 1:250,000 Landslide inventory. Timor-Leste (west), 2011 
* Timor Leste Landslide Inventory database, 2011

## 5.4 Selected Invited and Keynote talks

International 

* 3rd International Student Energy Summit, ISES 2013, Tronheim, Norway. June 2013.`r margin_note( "Keynote" )`
* 24th IGC,  Brisbane  Global Geoscience Initiative, August 2012 ``r margin_note("Keynote" )`
* IUGG, Melbourne, July, 2011`r margin_note("keynote" )`
* NGRI Jubilee Celebrations, October, 2011, Hyderabad, India ``r margin_note( "Keynote" )`
* International Himalayn geodynamics, Wadia Institute, November, 2011 `r margin_note( "Invited" )`
* IISC Bangalore, india, April, 2010 `r margin_note( "Invited" )`
* GLADE,  California, July, 2010 `r margin_note( "Invited" )`
* SOTA, Greece, September, 2010 `r margin_note( "Keynote" )` 
* Imperial College, London, June 2009, `r margin_note( "Invited" )`
* Janet Watson Meeing, London May 30th.2009, `r margin_note( "Invited" )`
* SERN, Dili, Timor 2009 `r margin_note( "Invited" )`
* Geomorphology2009, Melbourne, July 2009 `r margin_note( "Keynote" )`
* Ecole Normale Superieur, Paris, June, 2008 `r margin_note( "invited" )`
* Grenoble, July 2008  `r margin_note( "invited" )`
* Gordon Conference, Italy, August 2008   `r margin_note( "Keynote" )` 
* Thomson Conference, ETH, Zurich,  2007  `r margin_note( "Invited" )` 


National

* SGTSG at Thredbo, February 2014, `r margin_note("Keynote")`
* EEC Eenergy Efficiency Council, National conference 2013, Melbourne, December 2013 `r margin_note( "Keynote" )`
* AuScope Symposium, Building the Earth Observatory, Canberra, July 30th, 2013 `r margin_note( "Keynote" )`
* AAS New fellows, May 2013, Canberra `r margin_note( "Invited" )`
* Victoria's Energy Future: Prospects and challenges, Royal Society of Victoria, Melbourne Oct 23rd, 2013 `r margin_note( "Keynote" )`
* Australian Earth Science Convention, Canberra, 2010 `r margin_note( "Keynote" )`
* Australian Institute of Physics Conference, Canberra, 2005, `r margin_note( "Invited" )`

***
# 6. PhD student supervision and mentoring

## 6.1. PhD supervision

*	Shoahua Zhou, 1990,  ex-Senior Petroleum Engineering Consultant, Saudi Aramco, now retired
*	Jo Arnold, 1993,   Consultant, Magill Consulting, Adelaide
*	Ian Scrimgeour, 1993,  Director, Northern territory Geological Survey
*	Eike Paul, 1999,   Head of Geology RSE
*	Jon Teasdale, 1997,   Global strategist, Shell, Amsterdam
*	Bruce Schaefer, 1998,   Senior Lecturer, Macquarie University
*	Sandra McLaren, 2001 ,  Snr.Lecturer, University of Melbourne
*	Narelle Neumann, 2002,   Principal Scientist, Geoscience Australia
*	Victor Tokarev, 2003,   Senior Exploration Geologist, Santos, Adelaide
*	Mark Quigley, 2007 "Continental tectonics and landscape evolution in south-central Australia and southern Tibet" , AProf. University of Melbourne
*	Kim Ely, 2009 "Geochronology of Timor-Leste and seismo-tectonics of the southern Banda Arc",  Research fellow, Stonybrook University, USA
*	Sara Jakica, 2011, Multi-client business manager, HiSeis, Perth
* Jaeryul Shin, 2012 "Neogene vertical motions in intraplate settings: case studies from Australia and Korea",  Seoul, Korea
* Ben Harrison, 2015, "Measurement and modelling of heat flow in the Gippsland Basin", conultant GHD
* Steven Geroe, 2015, "Integration of specialist expertise in the Chinese renewable energy consultative drafting process: towards a rational-pluralist model", Melbourne School of Law
* Dylan McConnell, in progress, Impact of distributed generation on the Australian energy system
* Dimitri Lafleur,in progress, Migratory emissions in Australia
* Matthew Wood, in progress, Geomorhic evolution of eastern Bhutan
* Tamarah King, in progress, Palaeoearthquake proxies isn Australian landscapes.

## 6.2. Postdoctoral  supervision


* Prof Simon Turner,   currently Laureate Professor, Macquarie University 
* Dr David Coblentz,   currently Senior fellow, LANL, New Mexico 
* Prof Kurt Stuwe,   currently Professor, Graz University, Austria 
* Dr Geoff Fraser,   currently Geoscience Australia 
* Prof Martin Hand, currently head of School, University of Adelaide
* Dr Peter Haines,    currently Geological Survey WA 
* Dr Sandra Mclaren,    currently University of Melbourne 
* Prof David Egholm,   currently Aarhus University, Denmark 
* Dr Simon Bodorkos,    currently Geoscience Australia
* Dr Steve Boger,   currently Senior Lecturer, University of Melbourne
* Dr Kristin Morell,  currently Ass. Professor, University of Victoria, Canada
* Dr Tim Rawling,  currently CEO, AuScope, Melbourne 
* Dr Guangwei Li, currently Research Fellow, University of Melbourne
* Dr Januka Atanayke, currently Research Fellow, University of Melbourne

***
 
# 7. Public engagement

##  7.1 Written work

Op-eds in the national press. 


* Cherry-picking contrarian geologists tend to obscure scientific truth, December 31 2011
```{marginfigure} 
[the Australian](http://www.theaustralian.com.au/national-affairs/opinion/cherry-picking-contrarian-geologists-tend-to-obscure-scientific-truth/story-e6frgd0x-1226233605954)
```
* The scale of the effect we have on the planet is yet to sink in, May 23rd  2011  
```{marginfigure} 
[the Age](http://www.theage.com.au/it-pro/the-scale-of-the-effect-we-have-on-the-planet-is-yet-to-sink-in-20110522-1eyqk)
```
*  Fossil fuels will run out of gas when the solar revolution arrives, March 22nd  2011
```{marginfigure} 
[the Age](http://www.theage.com.au/it-pro/the-scale-of-the-effect-we-have-on-the-planet-is-yet-to-sink-in-20110522-1eyqk)
```
* Solar and wind power crucial for climate future, February 18th 2011
```{marginfigure} 
[ the Canberra Times]()
```
* Do renewable energy by the numbers, and it all adds up, June 24th 2010
```{marginfigure}  
[the Age](http://www.theage.com.au/it-pro/do-renewable-energy-by-the-numbers-and-it-all-adds-up-20100623-yywm)
```
* Geology points to dangers ahead, May 6th 2009
```{marginfigure}  
[the Australian](http://www.theaustralian.com.au/opinion/geology-points-to-dangers-ahead/story-e6frg6zo-1225710269931)
```


From its inception in 2011 to 2017, I was a columnist for the academic website -  [the Conversation](https://theconversation.com).  The `r tc.articles` posts on my column ([Energy an the Earth](https://theconversation.com/columns/mike-sandiford-228)) have been viewed  more than 840,000 times.

* Open season for our notion-building pollies, July 20, 2017.
```{marginfigure} 
[the Conversation](https://theconversation.com/open-season-for-our-notion-building-pollies-31943)
```
* The anatomy of an energy crisis - a pictorial guide, Part 3, March 20, 2017.
```{marginfigure} 
[the Conversation](https://theconversation.com/the-anatomy-of-an-energy-crisis-a-pictorial-guide-part-3-73693)
```
* The Australian gas market enters the “red zone”, as predicted, Marchy 10, 2017.
```{marginfigure} 
[the Conversation](https://theconversation.com/the-australian-gas-market-enters-the-red-zone-as-predicted-74314)
```
* The anatomy of an energy crisis - a pictorial guide, Part 2, February 20, 2017.
```{marginfigure} 
[the Conversation](https://theconversation.com/the-anatomy-of-an-energy-crisis-a-pictorial-guide-part-2-65206)
```
* The anatomy of an energy crisis - a pictorial guide, Part 1, February 13, 2017.
```{marginfigure} 
[the Conversation](https://theconversation.com/the-anatomy-of-an-energy-crisis-a-pictorial-guide-part-1-71789)
```
* We really must talk about gas, September 7th, 2016 
```{marginfigure} 
[the Conversation](https://theconversation.com/we-really-must-talk-about-gas-64213)
```
* Italy’s deadly earthquake is the latest in a history of destruction, August 24th, 2016 
```{marginfigure} 
[the Conversation](https://theconversation.com/italys-deadly-earthquake-is-the-latest-in-a-history-of-destruction-64384)
```
* Arrium’s requiem and the events of July 7th, August 18th, 2016 
```{marginfigure} 
[the Conversation](https://theconversation.com/arriums-requiem-and-the-events-of-july-7th-34275)
```
* Our planet is heating - the empirical evidence,  August 16th, 2016 
```{marginfigure} 
[the Conversation](https://theconversation.com/our-planet-is-heating-the-empirical-evidence-63990)
```
* Hazelwood highlights our tangled web of energy policy,  June 28th, 2016 
```{marginfigure} 
[the Conversation](https://theconversation.com/hazelwood-highlights-our-tangled-web-of-energy-policy-61640)
```
* Electricity prices, the election agenda and the case for bipartisanship,  June 22nd, 2016 
```{marginfigure} 
[the Conversation](https://theconversation.com/electricity-prices-the-election-agenda-and-the-case-for-bipartisanship-61297)
```
* A new normal, as Basslink finally resumes,  June 17th, 2016 
```{marginfigure} 
[the Conversation](https://theconversation.com/a-new-normal-as-basslink-finally-resumes-61195)
```
* The will of government is key to energy access. June 2nd, 2016 
```{marginfigure} 
[the Conversation](https://theconversation.com/the-will-of-government-is-key-to-energy-access-58332)
```
* Goodbye Northern lights, hello sunlight?. May 12th, 2016 
```{marginfigure} 
[the Conversation](https://theconversation.com/goodbye-northern-lights-hello-sunlight-58219)
```
* The Turnbull of old. May 10th, 2016
```{marginfigure} 
[the Conversation](https://theconversation.com/the-turnbull-of-old-59006)
```
* Raising Tibet. April 29th, 2016
```{marginfigure} 
[the Conversation](https://theconversation.com/raising-tibet-58483)
```
* On windmills and warships. April 25th, 2016
```{marginfigure} 
[the Conversation](https://theconversation.com/on-windmills-and-warships-46071)
```
* Are the Japanese and Ecuador earthquakes related?? April 19th, 2016
```{marginfigure} 
[the Conversation](https://theconversation.com/are-the-japanese-and-ecuador-earthquakes-related-57978)
```
* A precarious geological bargain? April 18th, 2016
```{marginfigure} 
[the Conversation](https://theconversation.com/a-precarious-geological-bargain-57903)
```
* Travelling with Timor Leste April 15th, 2016
```{marginfigure} 
[the Conversation](https://theconversation.com/travelling-with-timor-leste-57635)
```
* Who’s been our hottest PM? April 1st, 2016
```{marginfigure} 
[the Conversation](https://theconversation.com/whos-been-our-hottest-pm-57062)
```
* Praying for rain, November 6th  2015  
```{marginfigure} 
[the Conversation](https://theconversation.com/praying-for-rain-50085)
```
* Winds of change,  November 1st 2015 
```{marginfigure} 
[the Conversation](https://theconversation.com/winds-of-change-49341)
```
*  The science behind the Nepal earthquake
April 27th 2015
```{marginfigure} 
[the Conversation](https://theconversation.com/the-science-behind-the-nepal-earthquake-40835)
```
* Glimpsing a Tasmanian export opportunity, March 14th, 2015  
```{marginfigure} 
[the Conversation](https://theconversation.com/glimpsing-a-tasmanian-export-opportunity-38641)
```
* Yes minister, but …  January 30th 2015
```{marginfigure} 
[the Conversation](https://theconversation.com/yes-minister-but-36789)
```
* A crash in gas use is more likely than the forecast ‘shortage’
January 28  2015 
```{marginfigure} 
[the Conversation](https://theconversation.com/a-crash-in-gas-use-is-more-likely-than-the-forecast-shortage-36764)
```
* Coal seam gas is just the latest round in an underground war
December 10th 2014 
```{marginfigure} 
[the Conversation](https://theconversation.com/coal-seam-gas-is-just-the-latest-round-in-an-underground-war-35164)
```
* A record growth in electricity sector emissions, November 4th  2014
```{marginfigure} 
[the Conversation](https://theconversation.com/a-record-growth-in-electricity-sector-emissions-33772)
```
*  Repaying the emissions debt, September 8th  2014
```{marginfigure} 
[the Conversation](https://theconversation.com/repaying-the-emissions-debt-31399)
```
* Gas ain’t so green, according to BP, September 3rd  2014
```{marginfigure} 
[the Conversation](https://theconversation.com/gas-aint-so-green-according-to-bp-31055)
```
* How much will Tasmania pay for shorting the carbon price? July 13th   2014
```{marginfigure} 
[the Conversation](https://theconversation.com/how-much-will-tasmania-pay-for-shorting-the-carbon-price-29106)
```
* Will the real Greg Hunt please stand up? July 7th 2014
```{marginfigure} 
[the Conversation](https://theconversation.com/will-the-real-greg-hunt-please-stand-up-28834)
```
* Jacqui Lambie’s carbon tax dilemma – what is good for Tasmania?  July 4th  2014
```{marginfigure} 
[the Conversation](https://theconversation.com/jacqui-lambies-carbon-tax-dilemma-what-is-good-for-tasmania-28807)
```
* Has the death spiral for Australia’s electricity market begun? June 29th 2014
```{marginfigure} 
[the Conversation](https://theconversation.com/has-the-death-spiral-for-australias-electricity-market-begun-28581)
```
*  Another summer on the NEM, March 17th  2014 
```{marginfigure} 
[the Conversation](https://theconversation.com/another-summer-on-the-nem-24451)
```
*  The curious case of Caroline, March 12th  2014
```{marginfigure} 
[the Conversation](https://theconversation.com/the-curious-case-of-caroline-19084)
```
* So if the carbon tax is not working, then what is? December 9th  2013 
```{marginfigure} 
[the Conversation](https://theconversation.com/so-if-the-carbon-tax-is-not-working-then-what-is-21284)
```
* A “frack” in the bridge from coal to gas,  October 8th  2013
```{marginfigure} 
[the Conversation](https://theconversation.com/a-frack-in-the-bridge-from-coal-to-gas-18992)
```
*  Direct action to an emissions freefall, October 3rd  2013
```{marginfigure} 
[the Conversation](https://theconversation.com/direct-action-to-an-emissions-freefall-18830)
```
* Australian ‘grid’ story, August 6th 2013
```{marginfigure} 
[the Conversation](https://theconversation.com/australian-grid-story-16747)
```
* The great de-electrification,  August 4th 2013
```{marginfigure} 
[the Conversation](https://theconversation.com/the-great-de-electrification-16687)
```
*  How broken is the Government’s Carbon pricing mechanism? July 27th  2013
```{marginfigure} 
[the Conversation](https://theconversation.com/how-broken-is-the-governments-carbon-pricing-mechanism-16442)
```
* The black decade, July 11th 2013 
```{marginfigure} 
[the Conversation](https://theconversation.com/the-black-decade-15998)
```
* How clean are our energy policies? July 9th 2013  
```{marginfigure} 
[the Conversation](https://theconversation.com/how-clean-are-our-energy-policies-15926)
```
* Summer on the NEM, March 5th  2013 
```{marginfigure} 
[the Conversation](https://theconversation.com/summer-on-the-nem-12635)
```
* A lot of hot air in the coal to gas transition,  November 13th  2012 
```{marginfigure} 
[the Conversation](https://theconversation.com/a-lot-of-hot-air-in-the-coal-to-gas-transition-10719)
```
*  An incumbent industry, October 1st  2012,
```{marginfigure} 
[the Conversation](https://theconversation.com/an-incumbent-industry-9907)
```
* Who’s afraid of solar PV? August 21st  2012
```{marginfigure} 
[the Conversation](https://theconversation.com/whos-afraid-of-solar-pv-8987)
```
* The problem in the grid, August 16th  2012
```{marginfigure} 
[the Conversation](https://theconversation.com/the-problem-in-the-grid-8868)
```
* Power prices and the carbon tax: when will the sky fall in? July 18th  2012 
```{marginfigure} 
[the Conversation](https://theconversation.com/power-prices-and-the-carbon-tax-when-will-the-sky-fall-in-8308)
```
* One piddling light and the plummeting cost of wholesale electricity, July 12th  2012
```{marginfigure} 
[the Conversation](https://theconversation.com/one-piddling-light-and-the-plummeting-cost-of-wholesale-electricity-8125)
```
* If you think King Coal is dead, think again …, July 5th   2012 
```{marginfigure} 
[the Conversation](https://theconversation.com/if-you-think-king-coal-is-dead-think-again-8100)
```

* Our effect on the earth is real: how we’re geo-engineering the planet, June 16th 2011
```{marginfigure} 
[the Conversation](https://theconversation.com/our-effect-on-the-earth-is-real-how-were-geo-engineering-the-planet-1544)
```

## 7.2 Selected TV \& Radio interviews

* Hazelwood coal-fired power station to close in March 2017, ABC RN Drive with Patricia Karvelas, 3rd November 2016
```{marginfigure}
[ABC RN - link](http://www.abc.net.au/radionational/programs/drive/hazelwood-coal-station-to-close/7994082)
```
* Wind power cut costs 40 per cent during heatwave, ABC  Radio National Breakfast with Fran Kelly 27th Febraury, 2014, 
```{marginfigure}
[ABC RN - link](http://www.abc.net.au/radionational/programs/breakfast/wind-cut-power-cut-costs-40-during-heatwave-report/5287356)
```
* Unconventional gas - energy saviour or environmental problem, ABC RN Big Ideas with Paul Barclay, 6th November, 2013,
```{marginfigure}
[ABC RN - link](http://www.abc.net.au/radionational/programs/bigideas/unconventional-gas---energy-saviour-or-environmental-problem/4912820)
```
* Power closure plans threatened as brown coal booms,  ABC  Radio National Breakfast with Fran Kelly 9th August, 2012
```{marginfigure}
[ABC RN - link](http://www.abc.net.au/radionational/programs/breakfast/power-closure-plans-threatened-as-brown-coal-booms/4187384)
```
* Transformation in the Australian energy sector,  ABC  Radio National Breakfast with Fran Kelly 29th June, 2012
```{marginfigure}
[ABC RN - link](http://www.abc.net.au/radionational/programs/breakfast/transformation-in-the-australian-energy-sector/4099728)
```
* Australia moves north, ABC Radio National Late Night Live with Phillip Adams, 10th February 2004
* Australian Earthquakes, ABC  Radio National Breakfast with Peter Thompson, 5th June 2003,
```{marginfigure}
[ABC RN - link](http://www.abc.net.au/radionational/programs/breakfast/australian-earthquakes/3535158)
```

* Fractured future, May 5th 2005
```{marginfigure}
[ABC TV Catalyst - link](http://www.abc.net.au/catalyst/stories/s1360803.htm)
```

* Earthquake Study, ABC Radio National Breakfast with Peter Thompson, 20th December 2002 
```{marginfigure}
[ABC RN - link](http://www.abc.net.au/radionational/programs/breakfast/earthquake-study/3532510)
```

* Geothermal power operating in South Australia, ABC Science show,  June 1 2013, 

## 7.3 Public lectures

* [Intelligence Squared debates - Will coal-fired power soon be obsolete](http://www.wheelercentre.com/events/coal-fired-power-will-soon-be-obsolete), Wheeler Centre, Melbourne, October 18th 2014, `r margin_note( "Public debate" )`
* Womad Earthstation, Adelaide, October, 2011 `r margin_note( "Public lecture" )`
* Mawson lecture, Why oz quakes?, Hobart Tasmania `r margin_note( "Public lecture" )`


## 7.4 Independent commentary
*  Finding majesty in the earth's dynamics, July 14  2014
```{marginfigure} 
[the Age](http://www.theage.com.au/national/education/voice/finding-majesty-in-the-earths-dynamics-20140708-3bkll.html) 
 ```

* River deep, mountain high, July 8, 2013 
```{marginfigure} 
[SMH](http://www.smh.com.au/national/education/voice/river-deep-mountain-high-20130704-2pecq.html)
```
 * River deep, mountain high: New study reveals clues to lifecycle of world's iconic mountains, June 27 2013
```{marginfigure} 
[Science daily](http://www.sciencedaily.com/releases/2013/06/130627102631.htm)
```
*  Predicting the quake, April 18  2005 
```{marginfigure} 
[the Age](http://www.theage.com.au/news/Education-News/Predicting-the-quake/2005/04/15/1113509921667.html?from=moreStories)
``` 
* Asian earthquake risk suggested before tsunami disaster, January 26 2005
```{marginfigure} 
[New Scientist](https://www.newscientist.com/article/mg18524843-900-asian-earthquake-risk-suggested-before-tsunami-disaster/)
```
* Australia’s quake-ridden past is uncovered, June 7 2003
```{marginfigure} 
[New Scientist](https://www.newscientist.com/article/mg17823982-300-australias-quake-ridden-past-is-uncovered/)
```

